---
title: "TFM - FINAL SCRIPT"
author: "ROSAMUNDE HENDRICKS"
date: "2024-08-20"
output: html_document
---

#Loading Data
```{r}
```{r setup, include=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyr)
library(lme4)
library(tidyverse)
library(ggstatsplot)
library(gghalves)
library(car)
library(lmtest)
library(lmerTest)
library(nortest)
library(emmeans)

#Download Dataset 
Data <- read_excel('Data_CLS_US.xlsx')

```


#Demographics 
```{r}
```{r setup, include=FALSE}
###Mean and SD Age 
Data$age <- as.numeric(Data$age)
mean_age <- mean(Data$age, na.rm = TRUE)
sd_age <- sd(Data$age, na.rm = TRUE)
mean_age
sd_age

# Convert gender to numeric if it's not already
Data$gender_numeric <- as.numeric(as.character(Data$gender))

# Create indicator variables for each gender
Data$Male <- ifelse(Data$gender == 1, 1, ifelse(Data$gender == 2 | Data$gender == 3, 0, NA))
Data$Female <- ifelse(Data$gender == 2, 1, ifelse(Data$gender == 1 | Data$gender == 3, 0, NA))
Data$Others <- ifelse(Data$gender == 3, 1, ifelse(Data$gender == 1 | Data$gender == 2, 0, NA))

# Calculate the percentages for each gender
percentage_male <- mean(Data$Male, na.rm = TRUE) * 100
percentage_female <- mean(Data$Female, na.rm = TRUE) * 100
percentage_others <- mean(Data$Others, na.rm = TRUE) * 100

###Party Affiliation 
Affiliation <- table(Data$partyAffiliation)
print(Affiliation)
# Calculate Percentage
party_percentages <- prop.table(Affiliation) * 100
print(party_percentages)

#Plot Part Affiliation 
Party_aff <- data.frame(Party = factor(names(Affiliation), levels = c("1", "2", "3")),
                         Count = as.numeric(Affiliation))

ggplot(Party_aff, aes(x = Party, y = Count, fill = Party)) +
  geom_bar(stat = "identity", width = 0.6, color = "darkgray") + 
  geom_text(aes(label = Count), vjust = -0.5, size = 4) +
  labs(title = "Party Affiliation",
       x = "Party Affiliation",
       y = "Frequency") +
  scale_x_discrete(labels = c("1" = "Republican", "2" = "Democratic", "3" = "Independent")) +
  scale_fill_manual(values = c("1" = "darkred", "2" = "darkblue", "3" = "darkgreen")) +
  theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.line = element_line(color = "darkgrey"),
    plot.title = element_text(size = 16, hjust = 0.5, face = "bold"),  
    legend.position = "none"
  ) +
  coord_cartesian(ylim = c(0, 100))

```

#Manipulation Check 
```{r}
#Mani check 1: How accurate do you think the AI virtual assistant was in calculating the Moral Match of each news?
Data <- Data %>%
  mutate(Mani_check1 = as.numeric(ifelse(Mani_check1 == "1- Not accurate at all", 1, Mani_check1)))
#Mean value
mean_value <- mean(Data$Mani_check1, na.rm = TRUE)
sd_value1 <- sd(Data$Mani_check1, na.rm = TRUE)

#Mani check 2: To what extent did you believe that the AI virtual assistant was provinding real time Moral Match scores?
Data <- Data %>%
  mutate(Mani_check2 = ifelse(Mani_check2 == "1 - I did not believe it at all", 1,
                               ifelse(Mani_check2 == "5 - I completely believed it", 5, as.numeric(Mani_check2))))
#Mean value
mean_value2 <- mean(Data$Mani_check2, na.rm = TRUE)
sd_value2 <- sd(Data$Mani_check2, na.rm = TRUE)

#Mani check 3: How much did you trust the moral match score? 
Data <- Data %>%
  mutate(Mani_check3 = as.numeric(ifelse(Mani_check3 == "1- I did not trust it at all", 1, Mani_check3)))
#Mean value
mean_value3 <- mean(Data$Mani_check3, na.rm = TRUE)
sd_value3 <- sd(Data$Mani_check3, na.rm = TRUE)
```

#Creating Long format of Dataset and Means 
```{r}
#Long format
Data_long <- Data %>%
  pivot_longer(cols = starts_with(c("con", "lib", "neut")),
               names_to = "variable",
               values_to = "value") %>%
  separate(variable, into = c("type", "version", "morality"), sep = "_", convert = TRUE) %>%
  mutate(morality = as.factor(morality),
         PROLIFIC_PID = as.factor(PROLIFIC_PID))  


# Remove rows with NA values in the "value" column
Data_long_filtered <- Data_long %>%
  filter(!is.na(value))

###Means for the different political conditions (lib, con, neut by accuracy and readability)
Data_long_filtered <- Data_long_filtered %>%
  mutate(type_group = sub("\\d", "", type))

# Group by relevant variables and calculate means
averages <- Data_long_filtered %>%
  group_by(PROLIFIC_PID, version, type_group) %>%
  summarize(mean_value_pol = mean(value, na.rm = TRUE))

# Add mean values to the Data_long_filtered dataset
Data_long_filtered <- Data_long_filtered %>%
  left_join(averages, by = c("PROLIFIC_PID", "version", "type_group")) %>%
  mutate(mean_value_pol = coalesce(mean_value_pol, value))

# Group by relevant variables and calculate means
averages_mor <- Data_long_filtered %>%
  group_by(PROLIFIC_PID, version, type_group, morality) %>%
  summarize(mean_value_moral = mean(value, na.rm = TRUE))

# Add mean values to the Data_long_filtered dataset
Data_long_filtered <- Data_long_filtered %>%
  left_join(averages_mor, by = c("PROLIFIC_PID", "version", "type_group", "morality")) %>%
  mutate(mean_value_moral = coalesce(mean_value_moral, value))

```


#Political Orientation on Likelihood of Reading News Posts and Perceived Accuracy (Hypothesis 1)
```{r}
#"1" = "Republican", "2" = "Democrat", "3" = "Independent"

# Compare averages for "con" based on "partyAffiliation" variable
con_comparison <- Data_long_filtered %>%
  filter(type_group == "con") %>%
  group_by(PROLIFIC_PID, partyAffiliation) %>%
  summarize(value = mean(value, na.rm = TRUE))

# Compare averages for "lib" based on "partyAffiliation" variable
lib_comparison <- Data_long_filtered %>%
  filter(type_group == "lib") %>%
  group_by(PROLIFIC_PID, partyAffiliation) %>%
  summarize(value = mean(value, na.rm = TRUE))


                          ######################## Readability ########################

# Calculate grand mean and standard deviation for each level of "partyAffiliation" for "con" and "read" version
grand_summary_con <- Data_long_filtered %>%
  filter(type_group == "con", version == "read") %>%
  group_by(partyAffiliation) %>%
  summarize(
    grand_mean = mean(value, na.rm = TRUE),
    grand_sd = sd(value, na.rm = TRUE)
  )

# Calculate grand mean and standard deviation for each level of "partyAffiliation" for "lib" and "read" version
grand_summary_lib <- Data_long_filtered %>%
  filter(type_group == "lib", version == "read") %>%
  group_by(partyAffiliation) %>%
  summarize(
    grand_mean = mean(value, na.rm = TRUE),
    grand_sd = sd(value, na.rm = TRUE)
  )

# Combine the results for plotting
combined_grand_means_read <- rbind(
  mutate(grand_summary_con, type_group = "conservative"),
  mutate(grand_summary_lib, type_group = "liberal")
)

# Filter out rows with 'Independent' party affiliation
combined_grand_means_read <- combined_grand_means_read %>% filter(partyAffiliation != "3")

combined_grand_means_read$type_group <- recode(combined_grand_means_read$type_group, "conservative" = "Conservative", "liberal" = "Liberal")

# Plotting 
ggplot(combined_grand_means_read, aes(x = factor(partyAffiliation), y = grand_mean, fill = type_group)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = grand_mean - grand_sd, ymax = grand_mean + grand_sd), position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Party Affiliation", y = "Likelihood of Reading") +
  scale_x_discrete(labels = c("1" = "Republican", "2" = "Democratic")) +
  scale_fill_manual(values = c("Conservative" = "darkred", "Liberal" = "darkblue")) +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 10)) +
  labs(fill = "News Type") +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")  
  )

# Filter the dataset for the relevant conditions
filtered_data <- Data_long_filtered %>%
  filter(type_group %in% c("con", "lib"), version == "read", partyAffiliation %in% c(1, 2))

# Conduct ANOVA
anova_result <- aov(value ~ type_group * partyAffiliation, data = filtered_data)
summary(anova_result)

# Conduct post hoc tests (Tukey's HSD)
posthoc_result <- TukeyHSD(anova_result)
print(posthoc_result)



                          ######################## Accuracy ########################

# Calculate grand mean and standard deviation for each level of "partyAffiliation" for "con" and "accu" version
grand_summary_con_accu <- Data_long_filtered %>%
  filter(type_group == "con", version == "accu") %>%
  group_by(partyAffiliation) %>%
  summarize(
    grand_mean = mean(value, na.rm = TRUE),
    grand_sd = sd(value, na.rm = TRUE)
  )

# Calculate grand mean and standard deviation for each level of "partyAffiliation" for "lib" and "accu" version
grand_summary_lib_accu <- Data_long_filtered %>%
  filter(type_group == "lib", version == "accu") %>%
  group_by(partyAffiliation) %>%
  summarize(
    grand_mean = mean(value, na.rm = TRUE),
    grand_sd = sd(value, na.rm = TRUE)
  )

# Combine the results for plotting
combined_grand_means_accu <- rbind(
  mutate(grand_summary_con_accu, type_group = "conservative"),
  mutate(grand_summary_lib_accu, type_group = "liberal")
)

# Filter out rows with 'Independent' party affiliation
combined_grand_means_accu <- combined_grand_means_accu %>% filter(partyAffiliation != "3")

combined_grand_means_accu$type_group <- recode(combined_grand_means_accu$type_group, "conservative" = "Conservative", "liberal" = "Liberal")

# Plotting 
ggplot(combined_grand_means_accu, aes(x = factor(partyAffiliation), y = grand_mean, fill = type_group)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = grand_mean - grand_sd, ymax = grand_mean + grand_sd), position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Party Affiliation", y = "Perceived Accuracy") +
  scale_x_discrete(labels = c("1" = "Republican", "2" = "Democratic")) +
  scale_fill_manual(values = c("Conservative" = "darkred", "Liberal" = "darkblue")) +
  theme_minimal() +
  coord_cartesian(ylim = c(0, 10)) +
  labs(fill = "News Type") +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold")  
  )


# Filter the dataset for the relevant conditions
filtered_data_accu <- Data_long_filtered %>%
  filter(type_group %in% c("con", "lib"), version == "accu", partyAffiliation %in% c(1, 2))

# Conduct ANOVA
anova_result_accu <- aov(value ~ type_group * partyAffiliation, data = filtered_data_accu)
summary(anova_result_accu)

# Conduct post hoc tests (Tukey's HSD)
posthoc_result_accu <- TukeyHSD(anova_result_accu)
print(posthoc_result_accu)

```

#All Morality Conditions by News Type 
```{r}

subset_Data<- Data_long_filtered %>%
  select(PROLIFIC_PID, version, type_group, morality, partyAffiliation, value)

                              ######################## Readability ########################

#Create subset for "read"
subset_read <- subset_Data%>%
  filter(version == "read", partyAffiliation != 3)

# Define color labels
news_type_colors <- c("con" = "lightblue", "lib" = "lightpink", "neut" = "lightgreen")
color_labels <- c("con" = "Conservative", "lib" = "Liberal", "neut" = "Neutral")
facet_labels <- c("1" = "Republican", "2" = "Democrat")

# Create Plot 
ggplot(subset_read, aes(x = morality, y = value, color = type_group)) +
  geom_half_violin(aes(fill = type_group), trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7, color = news_type_colors[subset_read$type_group]) +
  geom_boxplot(width = 0.4, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 16,
    size = 3,
    position = position_dodge(0.8),
    aes(group = partyAffiliation),
    color = "black"
  ) +
  labs(
       x = "Morality",
       y = "Value") +
  facet_wrap(~partyAffiliation, scales = "free", labeller = as_labeller(facet_labels)) +
  scale_color_manual(name = "News Type", values = c("con" = "lightblue", "lib" = "lightpink", "neut" = "lightgreen"), labels = c("Conservative", "Liberal", "Neutral")) +
  scale_fill_manual(name = "News Type", values = c("con" = "lightblue", "lib" = "lightpink", "neut" = "lightgreen"), labels = c("Conservative", "Liberal", "Neutral")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



                              ########################  Accuracy  ########################

# Create subset for "accu"
subset_accu <- subset_Data%>%
  filter(version == "accu", partyAffiliation != 3)

# Create Plot 
ggplot(subset_accu, aes(x = morality, y = value, color = type_group)) +
  geom_half_violin(aes(fill = type_group), trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7, color = news_type_colors[subset_read$type_group]) +
  geom_boxplot(width = 0.4, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 16,
    size = 3,
    position = position_dodge(0.8),
    aes(group = partyAffiliation),
    color = "black"
  ) +
  labs(
       x = "Morality",
       y = "Value") +
  facet_wrap(~partyAffiliation, scales = "free", labeller = as_labeller(facet_labels)) +
  scale_color_manual(name = "News Type", values = c("con" = "lightblue", "lib" = "lightpink", "neut" = "lightgreen"), labels = c("Conservative", "Liberal", "Neutral")) +
  scale_fill_manual(name = "News Type", values = c("con" = "lightblue", "lib" = "lightpink", "neut" = "lightgreen"), labels = c("Conservative", "Liberal", "Neutral")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

#Add new variable Political match
```{r}
Data_long_filtered <- Data_long_filtered %>%
  mutate(political_match = case_when(
    type_group == "lib" & partyAffiliation == 1 ~ "mismatch",
    type_group == "lib" & partyAffiliation == 2 ~ "match",
    type_group == "con" & partyAffiliation == 1 ~ "match",
    type_group == "con" & partyAffiliation == 2 ~ "mismatch",
    type_group == "neut" & partyAffiliation %in% c(1, 2) ~ "neutral",
    TRUE ~ NA_character_
  ))

# Filter out rows with NA values in the "value" variable
Data_long_filtered_noNA <- Data_long_filtered %>%
  filter(!is.na(political_match))
```


#Mismatch by Political Match for Readability and Accuracy (Plots)
```{r}

                          ######################## Readability ########################
#Filter for "read" condition
Data_long_filtered_noNA_read <- Data_long_filtered %>%
  filter(!is.na(political_match), version == "read")

# Plot
ggplot(Data_long_filtered_noNA_read, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  stat_summary(fun.y = "mean", geom = "point", position = position_dodge(0.8), size = 3, shape = 16) +  # Add points for mean values
  labs(title = "Mean Value for Likelihood to Read for Morality Match by Political Match",
       x = "Political Match",
       y = "Mean Value",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "Match", "mismatch" = "Mismatch", "neutral" = "Neutral")) +
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5))

############## Filter the data for the level of "mismatch" in "political_match"
mismatch_data_read <- Data_long_filtered_noNA_read %>%
  filter(political_match == "mismatch")

# Plot for the level of "mismatch" separated by "morality"
ggplot(mismatch_data_read, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  labs(title = "Mean Value for Likelihood to Read for Morality Match by News Items (Mismatch)",
       x = "Political Match",
       y = "Value",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "Match", "mismatch" = "Mismatch", "neutral" = "Neutral")) +
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5))

# Filter the data for the level of "mismatch" in "political_match" and "read" version
read_mismatch_data <- Data_long_filtered_noNA %>%
  filter(political_match == "mismatch" & version == "read")

# Calculate mean values for each level of "political_match" and "morality" in "read" version
mean_values_read <- read_mismatch_data %>%
  group_by(political_match, morality) %>%
  summarize(mean_value = mean(value))

# Plot for the level of "mismatch" in "read" version, separated by "morality"
ggplot(read_mismatch_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_read, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x = "Morality Match for Political Mismatch Items",  
       y = "Likelihood of Reading",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free", switch = "x", labeller = labeller(morality = c(control = "Control", mismatch = "Mismatch", match = "Match"))) +  
  ylim(-3, 12.5) +  
  theme_minimal() +
  theme(axis.text.x = element_blank(),  
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")
                          ########################  Accuracy   ########################

#Filter for "accu" condition
Data_long_filtered_noNA_accu <- Data_long_filtered %>%
  filter(!is.na(political_match), version == "accu")

# Plot
ggplot(Data_long_filtered_noNA_accu, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  stat_summary(fun.y = "mean", geom = "point", position = position_dodge(0.8), size = 3, shape = 16) +  # Add points for mean values
  labs(title = "Mean Value for Accuracy for Morality Match by Political Match",
       x = "Political Match",
       y = "Mean Value",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),  
        plot.title = element_text(hjust = 0.5))

# Filter the data for the level of "mismatch" in "political_match" and "accu" version
accu_mismatch_data <- Data_long_filtered_noNA %>%
  filter(political_match == "mismatch" & version == "accu")

# Calculate mean values for each level of "political_match" and "morality" in "accu" version
mean_values_accu <- accu_mismatch_data %>%
  group_by(political_match, morality) %>%
  summarize(mean_value = mean(value))

# Plot for the level of "mismatch" in "accu" version, separated by "morality"
ggplot(accu_mismatch_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_accu, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x ="Political Match", 
       y = "Perceived Accuracy",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),  # Remove x-axis text
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")  

# Plot for the level of "mismatch" in "accu" version, separated by "morality"
ggplot(accu_mismatch_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_accu, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x ="Morality Match for Political Mismatch Items", 
       y = "Perceived Accuracy",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free", switch = "x", labeller = labeller(morality = c(control = "Control",mismatch = "Mismatch",match = "Match"))) +  # Use labeller to customize facet labels
  ylim(-3, 12.5) +  
  theme_minimal() +
  theme(axis.text.x = element_blank(),  
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")  


```


#Match by Political Match for Readability and Accuracy  (Plots)
```{r}

                          ######################## Readability ########################

# Filter the data for the level of "match" in "political_match"
match_data_read <- Data_long_filtered_noNA_read %>%
  filter(political_match == "match")

# Plot for the level of "match" separated by "morality"
ggplot(match_data_read, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  labs(title = "Mean Value for Likelihood to Read for Morality Match by News Items (Match)",
       x = "Political Match",
       y = "Value",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "Match", "mismatch" = "Mismatch", "neutral" = "Neutral")) +
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5))

# Filter the data for the level of "match" in "political_match" and "read" version
read_match_data <- Data_long_filtered_noNA %>%
  filter(political_match == "match" & version == "read")

# Calculate mean values for each level of "political_match" and "morality" in "read" version
mean_values_read_match <- read_match_data %>%
  group_by(political_match, morality) %>%
  summarize(mean_value = mean(value))

# Plot for the level of "match" in "read" version, separated by "morality"
ggplot(read_match_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_read_match, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x = "Morality Match for Political Match Items",  # Adjust x-axis label
       y = "Likelihood of Reading",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free", switch = "x", labeller = labeller(morality = c(control = "Control", mismatch = "Mismatch", match = "Match"))) +  
  ylim(-3, 12.5) +  
  theme_minimal() +
  theme(axis.text.x = element_blank(),  
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")

                          ########################  Accuracy   ########################

# Filter the data for the level of "match" in "political_match" and "accu" version
accu_match_data <- Data_long_filtered_noNA %>%
  filter(political_match == "match" & version == "accu")

# Calculate mean values for each level of "political_match" and "morality" in "accu" version
mean_values_accu_match <- accu_match_data %>%
  group_by(political_match, morality) %>%
  summarize(mean_value = mean(value))

# Plot for the level of "match" in "accu" version, separated by "morality"
ggplot(accu_match_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_accu_match, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x = "Political Match",
       y = "Perceived Accuracy",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),  # Remove x-axis text
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")

# Plot for the level of "match" in "accu" version, separated by "morality"
ggplot(accu_match_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_accu_match, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x = "Morality Match for Political Match Items",
       y = "Perceived Accuracy",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free", switch = "x", labeller = labeller(morality = c(control = "Control", mismatch = "Mismatch", match = "Match"))) +  
  ylim(-3, 12.5) +  
  theme_minimal() +
  theme(axis.text.x = element_blank(),  
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")

```

#Control by Political Match for Readability and Accuracy (Plots)
```{r}
# Filter the data for the level of "neutral" in "political_match" and "read" version
read_neutral_data <- Data_long_filtered_noNA_read %>%
  filter(political_match == "neutral")

# Calculate mean values for each level of "political_match" and "morality" in "read" version
mean_values_read_neutral <- read_neutral_data %>%
  group_by(political_match, morality) %>%
  summarize(mean_value = mean(value))

ggplot(read_neutral_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_read_neutral, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x = "Morality Match for Political Neutral Items",  # Adjust x-axis label
       y = "Likelihood of Reading",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free", switch = "x", labeller = labeller(morality = c(control = "Control", mismatch = "Mismatch", match = "Match"))) +  
  theme_minimal() +
  ylim(-3, 12.5) +  
  theme(axis.text.x = element_blank(),  # Remove x-axis text
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")


# Filter the data for the level of "control" in "political_match" and "accu" version
accu_neutral_data <- Data_long_filtered_noNA %>%
  filter(political_match == "neutral" & version == "accu")

# Calculate mean values for each level of "political_match" and "morality" in "accu" version
mean_values_accu_neutral <- accu_neutral_data %>%
  group_by(political_match, morality) %>%
  summarize(mean_value = mean(value))

# Plot for the level of "control" in "accu" version, separated by "morality"
ggplot(accu_neutral_data, 
       aes(x = political_match, y = value, color = morality, fill = morality)) +
  geom_half_violin(trim = FALSE, position = position_nudge(x = -0.3), scale = "width", alpha = 0.7, width = 0.5) +
  geom_jitter(position = position_jitter(width = 0.2), size = 2, alpha = 0.7) +
  geom_boxplot(width = 0.5, position = position_dodge(0.8), color = "black", fill = "white", alpha = 0.7) +
  geom_point(data = mean_values_accu_neutral, aes(x = political_match, y = mean_value), 
             position = position_dodge(0.8), color = "black", size = 3, shape = 16) +
  labs(
       x = "Morality Match for Political Neutral Items",
       y = "Perceived Accuracy",
       color = "Morality",
       fill = "Morality") +
  scale_x_discrete(labels = c("match" = "", "mismatch" = "", "neutral" = "")) +  # Remove x-axis labels
  scale_color_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  scale_fill_manual(values = c("match" = "lightblue", "mismatch" = "lightpink", "control" = "lightgreen"), name = "Morality") +
  facet_wrap(~morality, scales = "free", switch = "x", labeller = labeller(morality = c(control = "Control", mismatch = "Mismatch", match = "Match"))) +  
  theme_minimal() +
  ylim(-3, 12.5) +  
  theme(axis.text.x = element_blank(),  
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "none")
```

#Statistical Analysis (Mixed Models)
```{r}

                         ########################  Accuracy   ########################

#Make control and neutral the reference categories 
Data_long_filtered_noNA_accu$political_match <- as.factor(Data_long_filtered_noNA_accu$political_match)
Data_long_filtered_noNA_accu$morality <- relevel(Data_long_filtered_noNA_accu$morality, ref = "control")
Data_long_filtered_noNA_accu$political_match <- relevel(Data_long_filtered_noNA_accu$political_match, ref = "neutral")

# Fit the mixed-effects model
mixed_model_accu <- lmer(value ~ morality * political_match + (1 | PROLIFIC_PID),  
                         data = Data_long_filtered_noNA_accu)
summary(mixed_model_accu)

# Add confidence intervals to the fixed effects
confint(mixed_model_accu)

#Compare contrasts with emmeans
em_model_accu <- emmeans(mixed_model_accu,pairwise ~ morality|political_match )
em_model_accu
confint(em_model_accu)

                          ######################## Readability ########################

#Make control and neutral the reference categories 
Data_long_filtered_noNA_read$political_match <- as.factor(Data_long_filtered_noNA_read$political_match)
Data_long_filtered_noNA_read$morality <- relevel(Data_long_filtered_noNA_read$morality, ref = "control")
Data_long_filtered_noNA_read$political_match <- relevel(Data_long_filtered_noNA_read$political_match, ref = "neutral")


#Mixed-effects model
mixed_model_read_filtered <- lmer(value ~ morality * political_match + (1 | PROLIFIC_PID),  
                     data = Data_long_filtered_noNA_read)
summary(mixed_model_read_filtered)

# Add confidence intervals to the fixed effects
confint(mixed_model_read_filtered)

#Compare contrasts with emmeans
em_model_read <- emmeans(mixed_model_read_filtered,pairwise ~ morality|political_match )
em_model_read
confint(em_model_read)

```

#Model Assumption Checks 
```{r}
# Extract residuals and fitted values
residuals <- residuals(mixed_model_read_filtered)
fitted_values <- fitted(mixed_model_read_filtered)

# 1. Linearity
plot(fitted_values, residuals, 
     xlab = "Fitted Values", 
     ylab = "Residuals", 
     main = "Residuals vs Fitted Values")
abline(h = 0, col = "red")

lines(lowess(fitted_values, residuals), col = "blue")

# 2. Homoscedasticity (Constant Variance)
#Breusch-Pagan test
bptest(lm(residuals ~ fitted_values))

# 3. Independence of Errors
#Durbin-Watson test
dwtest(lm(residuals ~ fitted_values))

# 4. Normality of Errors
# Plot a Q-Q plot
qqnorm(residuals, main = "Q-Q Plot")
qqline(residuals, col = "red")

# Histogram of residuals
hist(residuals, breaks = 30, main = "Histogram of Residuals", xlab = "Residuals")

#Shapiro-Wilk test
shapiro.test(residuals)

#Anderson-Darling test
ad.test(residuals)

```



